---
title: "Conduits Data Visualization"
author: "Alice Lépissier"
output: html_document
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = TRUE)
#setwd("C:/cloudstorage/googledrive/Projects/Tax Justice Network/Consultancy 2 - summer 18/Risk-based IFF/Scripts/") # Alice work
setwd("D:/Google Drive/Projects/Tax Justice Network/Consultancy 2 - summer 18/Risk-based IFF/") # Alice laptop
```


```{r preamble, echo = FALSE, message = FALSE, warning = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# PREAMBLE                  ####
## ## ## ## ## ## ## ## ## ## ##

library(colorspace)
library(dplyr)
library(geosphere)
library(leaflet)
# devtools::install_github('ropenscilabs/rnaturalearth')
# library(rnaturalearth) 
# library(networkD3)
# devtools::install_github("timelyportfolio/parsetR")
library(parsetR)
library(RColorBrewer)
# library(rgdal)
library(xlsx)
```


```{r geodata, echo = FALSE, message = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# IMPORT GEOSPATIAL DATA    ####
## ## ## ## ## ## ## ## ## ## ##

centroids <- read.xlsx2("../Data/Codes_Masterlist.xlsx", sheetName = "Codes")
centroids <- subset(centroids, select = c(Country, Longitude, Latitude))
centroids$Country <- as.character(centroids$Country)
centroids$Longitude <- as.numeric(as.character(centroids$Longitude))
centroids$Latitude <- as.numeric(as.character(centroids$Latitude))

load("../Data/panelSJ.RData")
```

Hover on the maps for further information.

You can re-arrange the countries in the Sankey diagram alphabetically or by size of the flow, and by clicking and dragging them.

# Banking Positions

The countries with the greatest exposure to illicit financial flows in banking positions are Isle of Man, Luxembourg, and Macao (Special Administrative Region of China).
```{r banking, echo = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# FOR BANKING POSITIONS     ####
## ## ## ## ## ## ## ## ## ## ##

conduits <- c("Isle of Man", "Luxembourg", "Macao")
```


## Claims
```{r Claims, echo = FALSE}
# .. Claims ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         Claims))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$Claims))
viz$Claims <- viz$Claims /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$Claims
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.Claims}"),
       tension = 0.5)
```


## Liabilities
```{r Liabilities, echo = FALSE}
# .. Liabilities ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         Liabilities))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$Liabilities))
viz$Liabilities <- viz$Liabilities /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$Liabilities
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.Liabilities}"),
       tension = 0.5)
```


# Direct Investment

The countries with the greatest exposure to illicit financial flows in Foreign Direct Investment (FDI) are Luxembourg, Bermuda, Samoa, Mauritius, and the Marhshall Islands.
```{r directinv, echo = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# FOR DIRECT INVESTMENT     ####
## ## ## ## ## ## ## ## ## ## ##

conduits <- c("Luxembourg", "Bermuda", "Samoa", "Mauritius", "Marshall Islands")
```


## Inward
```{r DII, echo = FALSE}
# .. Inward ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         DII))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$DII))
viz$DII <- viz$DII /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$DII
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.DII}"),
       tension = 0.5)
```


## Outward (derived)
```{r DIdO, echo = FALSE}
# .. Outward (derived) ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         DIdO))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$DIdO))
viz$DIdO <- viz$DIdO /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$DIdO
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.DIdO}"),
       tension = 0.5)
```


# Portfolio Investment

The countries with the greatest exposure to illicit financial flows in portfolio positions are Bermuda, Luxembourg, Marshall Islands, Ireland, and Mauritius.
```{r portinv, echo = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# FOR PORTFOLIO INVESTMENT  ####
## ## ## ## ## ## ## ## ## ## ##

conduits <- c("Bermuda", "Luxembourg", "Marshall Islands", "Ireland", "Mauritius")
```


## Assets
```{r PIA, echo = FALSE}
# .. Assets ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         PIA))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$PIA))
viz$PIA <- viz$PIA /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$PIA
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.PIA}"),
       tension = 0.5)
```


## Liabilities (derived)
```{r PIdL, echo = FALSE}
# .. Liabilities (derived) ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         PIdL))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$PIdL))
viz$PIdL <- viz$PIdL /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$PIdL
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.PIdL}"),
       tension = 0.5)

```


# Trade

The countries with the greatest exposure to illicit financial flows in trade are Hong Kong, Singapore, Belgium, Hungary, and Vietnam.
```{r trade, echo = FALSE}
## ## ## ## ## ## ## ## ## ## ##
# FOR TRADE                 ####
## ## ## ## ## ## ## ## ## ## ##

conduits <- c("Hong Kong", "Singapore", "Belgium", "Hungary", "Vietnam")
```


## Exports
```{r Export, echo = FALSE}
# .. Exports ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         Export))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$Export))
viz$Export <- viz$Export /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$Export
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

# cols <- rainbow_hcl(5)
# pal <- colorFactor(brewer.pal(4, "Set2"), flows$origins)
# Use Parset colors
cols <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd")
pal <- colorFactor(cols, flows$origins)
  
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.Export}"),
       tension = 0.5)
```


## Imports
```{r Import, echo = FALSE}
# .. Imports ####
viz <- subset(panelSJ, year == 2015,
              select = c(reporter, partner,
                         pSecrecyScore,
                         Import))
viz <- subset(viz, reporter %in% conduits)
viz <- subset(viz, !is.na(viz$Import))
viz$Import <- viz$Import /10^6

viz <- viz %>%
  left_join(centroids, by = c('reporter' = 'Country')) %>%
  left_join(centroids, by = c('partner' = 'Country'))
viz <- na.omit(viz)

viz$secrecy <- (10-1)/(max(viz$pSecrecyScore)-min(viz$pSecrecyScore)) * (viz$pSecrecyScore-min(viz$pSecrecyScore)) + 1
# Map variable onto 1-10 range
# range(viz$secrecy)

flows <- gcIntermediate(viz[,5:6], viz[,7:8], sp = TRUE, addStartEnd = TRUE)

flows$counts <- viz$Import
flows$origins <- viz$reporter
flows$destinations <- viz$partner
flows$secrecy <- viz$secrecy
flows$pSecrecyScore <- viz$pSecrecyScore

hover <- paste0(flows$origins, " to ", 
                flows$destinations, ": ",
                "$",
                format(round(flows$counts, 0), big.mark = ",", trim = T),
                " million",
                "; ",
                flows$destinations, " secrecy score: ",
                flows$pSecrecyScore)

cols <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd")
pal <- colorFactor(cols, flows$origins)
leaflet() %>%
  addProviderTiles("CartoDB.Positron") %>%
  addPolylines(data = flows, weight = ~secrecy, label = hover, 
               group = ~origins, color = ~pal(origins)) %>%
  addLayersControl(overlayGroups = unique(flows$origins), 
                   options = layersControlOptions(collapsed = FALSE)) %>%
  hideGroup(conduits[-1])

parset(viz, dimensions = c('reporter', 'partner'),
       value = htmlwidgets::JS("function(d){return d.Import}"),
       tension = 0.5)
```